---
title: "simpleRegress"
author: "Leslie Johnson"
date: "Summer 2021"
output: 
  html_document:
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## make a simple regression model

```{r}
bears <- read.csv(file="BEARS.csv",header = TRUE)
```

# NECK
## Model LENGTH ~ NECK  this is an example  

```{r}
simp <- lm(LENGTH~NECK,data=bears)
plot(LENGTH~NECK,data=bears)
abline(simp)
summary.lm(simp)
```


# HEADWTH
## Model LENGTH ~ HEADWTH

```{r}
simpHW <- lm(LENGTH~HEADWTH,data=bears)
plot(LENGTH~HEADWTH,data=bears)
abline(simpHW)
summary.lm(simpHW)
```

# HEADLEN
## Model LENGTH ~ HEADLEN

```{r}
simpHL <- lm(LENGTH~HEADLEN,data=bears)
plot(LENGTH~HEADLEN,data=bears)
abline(simpHL)
summary.lm(simpHL)
```

# WEIGHT
## Model LENGTH ~ WEIGHT

```{r}
simpWT <- lm(LENGTH~WEIGHT,data=bears)
plot(LENGTH~WEIGHT,data=bears)
abline(simpWT)
summary.lm(simpWT)
```

# CHEST
## Model LENGTH ~ CHEST

```{r}
simpCT <- lm(LENGTH~CHEST,data=bears)
plot(LENGTH~CHEST,data=bears)
abline(simpCT)
summary.lm(simpCT)
```

## now predict the length of a bear who has a neck of 17, 22 and 26


```{r}
new <- data.frame(NECK=c(17,13,9))
predict(simp,new)
predict(simp,new,se.fit=TRUE)
```
## Surely there is another variable that can better predict LENGTH than NECK. Find one and compare its performance to that of neck by it value of Adjusted-Rsquared (bigger is better).

